Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h, v)$.

>>>>

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $\bm{t}[k-1] = h'$ must intersect with $v$ (because $\bm{t}$ is a result tuple of the $(k-1)$-SJ). If $p$ is the intersection point between $h$ and $v$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment from the left endpoint of $h'$ to $p$.
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r_{k-2} \in R_{k-2} \mid \text{ $r_{k-2}$ contains the effective} \nn \\
    && \text{horizontal segment of $\bm{t}$}   \}
    \nn
}
The above definition should not be confused with \eqref{eqn:contained}, where the $\contained$ function takes a horizontal segment as the input.

\begin{lemma} \label{lmm:hv:type2:properties}
    For each $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, we have:
        \myenums{
            \item $\contained_{R_{k-2}}(\bm{t}) \ne \emptyset$.

            \item Denote by $h$ the full segment of $\bm{t}[k-1]$. 
            For any $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$, the $k$-tuple $(\bm{t}[1], ..., \bm{t}[k-3], r_{k-2}, h, \bm{t}[k])$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.

            \item If the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.
        }
\end{lemma}
